Habitat edges affect tree diversity more than biomass regeneration in a reforested wet neotropical timber plantation

### 2023-03-28 article/merge.Rmd
push link
minor

<!-- journals: J [Appl] Ecol (6.8), J [Appl] Veg Sci (3.4), Basic Appl Ecol (3.7), Biotropica (2.5), J Forestry Res (2.2), J Trop Ecol (1.3), Small-scale Forestry (1.3), Eco Evo -->

@@

***Correspondence**:  
Nicholas Medina, nmedina@umich.edu, https://orcid.org/0000-0001-5465-3988

>>>>

@@

***Correspondence**:  
Nicholas Medina, nmedina@umich.edu, [https://orcid.org/0000-0001-5465-3988](https://orcid.org/0000-0001-5465-3988)
